Apropos Replacement: Development of a full text search tool for man pages \newline (Initial Outline)

### 2011-12-26 paper.tex
Improve abstract

Traditionally, \textit{apropos} [1] has been there to act as a search
interface but to a large extent it hasn't really lived up to it's expectation.
\textit{apropos} was
developed in the early days of Unix when computing resources were scarce and
that is the primary reason for its minimalistic and simple design.

In this paper, the limitations of the traditional implementation of
\textit{apropos} are discussed along with brief details of how these were overcome as part of this project.
Additionally, we compare and contrast our approach with other modern implementations available out there.

>>>>

Traditionally, \textit{apropos} [1] has been there to act as a search
interface but to a large extent it hasn't really lived up to it's expectation.
\textit{apropos} was
developed in the early days of Unix when computing resources were scarce and
that is the primary reason for its minimalistic and simple design. The biggest
limitation of \textit{apropos} is it's limited search capabilities besides
man others.

We worked on fixing this by writing a new implementation of \textit{apropos} As part of \emph{Google Summer of Code 2011} [17]. The main goal of this project was
the development of a full text search tool for man pages.

In this paper, the limitations of the traditional implementation of apropos
are discussed along with brief details of how these were overcome as part of
this project. Additionally, we compare and contrast our approach with other
modern implementations available out there.
